---
title: "Analytics For Beginners"
author: "Rajat Shrivastav"
date: "October 3, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library('readxl')
library('stringr')  #To remove the asterisk
```


#lets first get the Data in
```{r}
rahul<-read_excel('C:\\Users\\1500202\\Documents\\NEW_R_Scripts\\Cricket_Data-2.xlsx',sheet="Rahul")
saurav<-read_excel('C:\\Users\\1500202\\Documents\\NEW_R_Scripts\\Cricket_Data-2.xlsx',sheet="Saurav")
```

Lets look at the structure
```{r}
str(rahul)
str(saurav)
```

Lets have the view of the data
```{r}
View(rahul)
```

Lets start with removing asterisk from the runs Scored column
```{r}
rahul$`Runs Scored`<-str_replace(rahul$`Runs Scored`,'\\*','')
saurav$`Runs Scored`<-str_replace(saurav$`Runs Scored`,'\\*','')
```

Let's remove the versus "v " from the opposition column
```{r}
rahul$Opposition<-gsub("^.{0,2}", "",rahul$Opposition)
saurav$Opposition<-gsub("^.{0,2}", "",saurav$Opposition)
```

NOw view the data
```{r}
View(rahul)
View(saurav)
```

Remove the DNB and TDNB from the dataset as these are the matches where they didn't bat

```{r}
rahul<-subset(rahul,`Runs Scored`!='DNB' & `Runs Scored`!='TDNB')
saurav<-subset(saurav,`Runs Scored`!='DNB' & `Runs Scored`!='TDNB')
```

Now from the Results remove the "tied" and "n/r" matches as they can't help in our analytics

```{r}
rahul<-subset(rahul,Result!='tied' & Result!='n/r')
saurav<-subset(saurav, Result!='tied' & Result!='n/r')
```

Converting the result variable to '1' or '0' based on a Win or a lose
```{r}
rahul$Result[rahul$Result=='won']<-1
rahul$Result[rahul$Result=='lost']<-0
saurav$Result[saurav$Result=='won']<-1
saurav$Result[saurav$Result=='lost']<-0
```

Converting the runs scored into numeric column 
```{r}
rahul$`Runs Scored`<-as.numeric(rahul$`Runs Scored`)
saurav$`Runs Scored`<-as.numeric(saurav$`Runs Scored`)
rahul$Result<- as.numeric(rahul$Result)
saurav$Result<-as.numeric(saurav$Result)
```




Last look into the dataset before applying the model.
```{r}
str(rahul)
str(saurav)
str(rahul$`Runs Scored`)
```



Building a logistic Model
```{r}
smodel3<-glm(formula= Result ~ `Runs Scored`, family="binomial", data = rahul)
summary(smodel3)
smodel4<-glm(formula= Result ~ `Runs Scored`, family="binomial", data = saurav)
summary(smodel4)
```

Making a matrix of calculated probablity of winning.
```{r}
glm.probs1 <- predict(smodel3,type = "response")
glm.probs2 <- predict(smodel4,type = "response")
glm.probs1[1:5]
glm.probs2[1:5]
length(glm.probs1)
length(glm.probs2)
```
 
Now once we have the calculated probabities with us we will make a new column vector for Win or loss

```{r}
glm.pred1 <- ifelse(glm.probs1 > 0.5, "Win", "Loss")  #for Rahul
glm.pred2 <- ifelse(glm.probs2 > 0.5, "Win", "Loss")  #for Saurav
#View(glm.pred1)
#View(glm.pred2)
length(glm.pred1)
length(glm.pred2)
```

Now to get how many matched did the model predicted win for Saurav Ganguly we could use glm.pred2
```{r}
a<-table(glm.pred1)
b<-table(glm.pred2)
a
b
```

lets look at the dimensions
```{r}
dim(rahul)
dim(saurav)
```

To get chitest value
```{r}
anova(smodel4,test='Chisq')
```































